AIR4Children: Artificial Intelligence and Robotics for Children

### 2021-03-08 slides/main.tex
polishes maketitle
re-organise layout of the slides
add Leticia in the coauthors

\title{air4children: Artificial Intelligence and Robotics for Children}
%\subtitle{...}
\author{
R. Montenegro,
E. Corona,
D. Badillo-P\'erez,
A. Mandujano,
D. Cruz,
{\bf Miguel Xochicale}
}
\date{
Workshop Child-Robot Interaction \& Child's Fundamental Rights at {\bf \#HRI2021} \\
March 08, 2021
}
\institute{
	\faEnvelope   air4children@gmail.com \\
	\faGithubAlt @air4children \faTwitter @air4children  
		}

@@

\input{sources/intro}
\input{sources/air4children}
\input{sources/conclusions-future-work}

\begin{frame}[standout]
  Thanks \\
  Questions?
\end{frame}

>>>>

\title{AIR4Children: Artificial Intelligence and Robotics for Children}
%\subtitle{...}
\author{
R. Montenegro,
E. Corona,
D. Badillo-P\'erez,
A. Mandujano,
L. V\'azquez,
D. Cruz,
{\bf Miguel Xochicale}
}
\date{
Workshop on Child-Robot Interaction \& Child's Fundamental Rights at {\bf \#HRI2021} \\
March 08, 2021
}
\institute{
	\faEnvelope   air4children@gmail.com \\
	\faGithubAlt @air4children \faTwitter @air4children  
		}

@@

\input{sources/introduction}
\input{sources/air4children}
\input{sources/conclusions-future-work}

%\begin{frame}[standout]
%  Thanks \\
%  Questions?
%\end{frame}

### 2021-03-08 slides/sources/air4children.tex

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Teaching Materials based on Montessori Education and Spiral Learning}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
{
\paper{Elkin M., Sullivan A, Bers 2014 in Journal of Informantion and Technology}
\begin{frame}{Adopting Montessori Education in AIR4Children curriculum} 
  \vspace{3mm}
  \it{"The hand is the instrument of the mind."} Dr. Maria Montessori (1970-1952).
  \vspace{2mm}
    \begin{figure}
        \centering
        \includegraphics[width=1.0\textwidth]{./figures/montessori/versions/drawing-v00.png}
        %\caption{}
      \end{figure}
\end{frame}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
{
\paper{Mohammad T. et al., 2017; Harden R. M. 1999 in Journal of Medical Teacher}
\begin{frame}{Adopting Spiral Learning Methods in AIR4Children curriculum}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Adopting Montessori Education and Spiral Learning}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
{
\paper{Elkin M., Sullivan A, Bers 2014 in Journal of Informantion and Technology}
\begin{frame}{Adopting Montessori Education in the curriculum of AIR4Children } 
  \vspace{3mm}
  \it{"The hand is the instrument of the mind."} Dr. Maria Montessori (1970-1952).
  \vspace{2mm}
    \begin{figure}
        \centering
        \includegraphics[width=1.0\textwidth]{./figures/montessori/versions/drawing-v00.png}
        %\caption{}
      \end{figure}
\end{frame}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
{
\paper{Mohammad T. et al., 2017; Harden R. M. 1999 in Journal of Medical Teacher}
\begin{frame}{Adopting Spiral Learning Methods in the curriculum of AIR4Children}
